Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-23 Tex/Old text/chapters/chapter04.tex
thesis updated text

%------------------------------------------
\section{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
Our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.

@@

The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{esbmcverifh5.png}
\centering
\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
\label{fig:esbmcverifhouse5}
\end{figure}

@@

There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.

In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system. We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems. However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) 
and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.

@@

We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.

\textit{Model precision:} each component of the PV system is mathematically modeled, and the precision of the proposed method depends on the precision of that particular model. 
The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.

\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.

\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.

>>>>

%------------------------------------------
\section{Objectives and Setup}
\label{sec:setup}
%------------------------------------------

The experimental evaluation aims to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.

@@

The description of the experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.

@@

\begin{figure}[h]
\includegraphics[width=0.65\textwidth]{esbmcverifh5.png}
\centering
\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
\label{fig:esbmcverifhouse5}
\end{figure}

@@

There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t. of proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that the proposed approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.

In order to validate the possible flaw from house 5, it was surveyed the owner of the 1,200 W system. It was identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems. However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) 
and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.

@@

At this Chapter, it was reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified five threats to the validity of the results that can further be assessed.

\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.

\textit{Time step:} The run-time complexity of the proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.

\textit{Case studies:} The case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.

\textit{Simulation Tool:} Only HOMER Pro was used. The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.

\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\cite{Temperature, Irradiance}. However, considering that riverside communities do not have weather stations, the data used in the present study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data. Therefore, the most accurate should be the use of weather stations in each location.

### 2019-07-23 Tex/Old text/chapters/chapter05.tex
thesis updated text

We have performed seven stand-alone PV system case studies to evaluate 
our proposed synthesis approach, as described in the first column of 
Table~\ref{tab1} (named Specification). These case studies were defined 
based on usual electrical load found in riverside communities of the 
Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

@@

Our evaluation aims to answer two experimental questions:

@@

\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?

@@

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
The experiments were performed with a predefined timeout of $240$ minutes.

@@

%---------------------------------------------------------------------------
\section{Results}  
%---------------------------------------------------------------------------

CPAchecker was able to synthesize the optimal sizing in six 
out of seven case studies: the result was produced within 
the time limit, which varied from $134.71$ to $235.75$ minutes. 
Only case study $7$ led to a \textit{timeout} result, i.e., 
it was not solved within $240$ minutes. However, if we remove 
this timeout limitation from CPAchecker, the verifier is 
able to solve the optimization in $44.97$ hours. 
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. %The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.

CBMC and ESBMC are unable to produce any conclusive result. 
Situations of \textit{internal failure}, \textit{timeout}, 
or \textit{out of memory} occurred; this partially answers 
the \textit{EQ2}. Note that the internal failure presented 
by ESBMC was a Z3 solver issue (a bug); this will demand 
an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
if we remove the timeout from ESBMC with the SMT solver Boolector, 
then the verifier is able to obtain the automated synthesis 
in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.

Related to HOMER Pro, it was able to evaluate six case studies, 
and within a time shorter than $30$ seconds, which was much 
faster than our automated synthesis tool (cf.~\textit{EQ2}). 
Case study $3$ was not possible to be simulated since HOMER Pro 
does not have the feature of adjusting the battery autonomy, i.e., 
the tool always tries to feed with electricity the given load 
during $365$ days/year. We have also noted other HOMER Pro drawbacks:

@@

Comparing the results between the formal synthesis with CPAchecker 
and HOMER Pro, we observed that most results are quite similar, 
in terms of technical solution and cost (cf. Table~\ref{tab1}).

@@

However, there exists a huge divergence in case study $2$, 
where the costs presented by HOMER Pro were $54$\% higher 
than our automated synthesis tool, probably because the 
operation and maintenance costs assumed by our automated 
synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were 
bigger in HOMER Pro than with our formal synthesis approach, 
and that discrepancy is not easy to address without some real 
systems validation. The mathematical models are different and 
particular parameters can be tuned as well in each approach, 
and that can justify the difference, which was presented in all 
the case studies. As comparative, let's consider case study $1$: 
the optimal solution provided by HOMER Pro demands $7$ $\times$ 
more PV panels than the solution presented by our synthesis tool, 
and HOME Pro does not show the arrangement of arrays 
(i.e., the number of series and parallel PV panels); 
the battery bank presented by HOMER Pro provides $500.4$ Ah 
of capacity ($6 \times 83.4$), while our synthesis tool 
presented an optimal solution with $420$ Ah of total capacity 
($4 \times 105$).

Just to compare the results obtained from the optimization 
with the real-world, the authors had four PV systems deployed 
and monitored since June $2018$ in a riverside community 
in the Amazonas State in Brazil, with similar demands 
presented by case studies $1$, $4$, $5$, and $6$, 
always with a $3$ $\times$ $325$ W ($3$S) panels and 
$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
lead-acid batteries. These solutions are more close 
to the result presented by our formal synthesis 
approach than HOMER Pro, thereby showing that our 
solution is sound, which answers \textit{EQ1}.

Related to the inverters, HOMER Pro suggests a value in 
kW very close to the peak of every case study, and it 
is just a reference value and not a commercial value of 
the employed inverter. Our synthesis tool, however, 
presents inverters that are commercial and can be found 
off-the-shelf. Therefore is a PRO to the formal synthesis method.

Concerning to charge controllers, as we reported in 
the previous section, HOMER Pro does not include it 
as an explicit equipment in its mathematical model, 
only our synthesis tool presents a commercial controller 
and includes it during the cost analysis. Therefore, 
the formal synthesis method presents more reliable results than
HOME Pro.

Case study $7$ was not solved by our synthesis tool 
within the time limit established during the experimental 
phase. Case study $3$ was not possible to simulate in HOMER Pro, 
because its restriction does not allow one to set the battery autonomy, 
thus resting both without parameters to comparative.

Summarizing, our synthesis tool is capable to present a 
solution, which is far detailed and close to the commercial 
reality than the solution presented by HOMER Pro. 
In particular, our automated synthesis method 
can provide all the details of every component of 
a PV system solution, with complete electrical details 
from data sheet of manufacturers, including 
the model of the component, nominal current and voltage. 
In this respect, even the name of the manufacturer 
can be presented (in Table~\ref{tab1} it was removed 
to avoid some advertising).
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

@@

We have reported a favorable assessment of our formal synthesis method. 
Nevertheless, we have also identified three threats to the validity 
of our experimental results, which can be further assessed and 
constitute future work: ($1$) improvement of the power reliability 
analysis: to include loss of load probability or loss of power 
supply probability, which can make the analysis more accurate; 
($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
however, a broad analysis from other isolated areas must be 
performed in order to make the optimization general in terms 
of applicability; ($3$) to deploy at the field some PV systems 
sized using our synthesized results in order to validate it.

>>>>

It was performed seven stand-alone PV system case studies to evaluate the proposed synthesis approach:

\begin{itemize}
\item Case Study 1: Power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h;
\item Case Study 2: Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h;
\item Case Study 3: Power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h;
\item Case Study 4: Power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h;
\item Case Study 5: Power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h;
\item Case Study 6: Power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h;
\item Case Study 7: Power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48h.
\end{itemize}

These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.

@@

The evaluation aims to answer two experimental questions:

@@

\item[EQ1] \textbf{(soundness)} does the proposed automated synthesis approach provide correct results?

@@

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), 
with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
The experiments were performed with a predefined time out of $240$ minutes.

@@

%---------------------------------------------------------------------------
\section{Results}  
\label{sec:synthesisresults}
%---------------------------------------------------------------------------

The results are presented at Table~\ref{tab1}.

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

CPAchecker was able to synthesize the optimal sizing in six 
out of seven case studies: the result was produced within 
the time limit, which varied from $134.71$ to $235.75$ minutes. 
Only case study $7$ led to a \textit{time out} result, i.e., 
it was not solved within $240$ minutes. However, if it is remove 
this time out limitation from CPAchecker, the verifier is 
able to solve the optimization in $44.97$ hours. 
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. %The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.

CBMC and ESBMC are unable to produce any conclusive result. 
Situations of \textit{internal failure}, \textit{time out}, 
or \textit{out of memory} occurred; this partially answers 
the \textit{EQ2}. Note that the internal failure presented 
by ESBMC was a Z3 solver issue (a bug); this will demand 
an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
if it is removed the time out from ESBMC with the SMT solver Boolector, 
then the verifier is able to obtain the automated synthesis 
in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.

Related to HOMER Pro, it was able to evaluate six case studies, 
and within a time shorter than $30$ seconds, which was much 
faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). 
Case study $3$ was not possible to be simulated since HOMER Pro 
does not have the feature of adjusting the battery autonomy, i.e., 
the tool always tries to feed with electricity the given load 
during $365$ days/year.

It was also noted other HOMER Pro drawbacks:

@@

Comparing the results between the formal synthesis with CPAchecker 
and HOMER Pro, it was observed that most results are quite similar, 
in terms of technical solution and cost (cf. Table~\ref{tab1}).

@@

However, there exists a huge divergence in case study $2$, 
where the costs presented by HOMER Pro were $54$\% higher 
than the automated synthesis tool, probably because the 
operation and maintenance costs assumed by the automated 
synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were 
bigger in HOMER Pro than with the formal synthesis approach, 
and that discrepancy is not easy to address without some real 
systems validation. The mathematical models are different and 
particular parameters can be tuned as well in each approach, 
and that can justify the difference, which was presented in all 
the case studies. As comparative, let's consider case study $1$: 
the optimal solution provided by HOMER Pro demands $7$ $\times$ 
more PV panels than the solution presented by the synthesis tool, 
and HOME Pro does not show the arrangement of arrays 
(i.e., the number of series and parallel PV panels); 
the battery bank presented by HOMER Pro provides $500.4$ Ah 
of capacity ($6 \times 83.4$), while the synthesis tool 
presented an optimal solution with $420$ Ah of total capacity 
($4 \times 105$).

Just to compare the results obtained from the optimization 
with the real-world, the authors had four PV systems deployed 
and monitored since June $2018$ in a riverside community 
in the Amazonas State in Brazil, with similar demands 
presented by case studies $1$, $4$, $5$, and $6$, 
always with a $3$ $\times$ $325$ W ($3$S) panels and 
$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
lead-acid batteries. These solutions are more close 
to the result presented by the proposed formal synthesis 
approach than HOMER Pro, thereby showing that the 
solution is sound, which answers \textit{EQ1}.

Related to the inverters, HOMER Pro suggests a value in 
kW very close to the peak of every case study, and it 
is just a reference value and not a commercial value of 
the employed inverter. The proposed synthesis tool, however, 
presents inverters that are commercial and can be found 
off-the-shelf. Therefore is a PRO to the formal synthesis method.

Concerning to charge controllers, as it was reported in 
the section~\ref{sec:synthesisresults}, HOMER Pro does not include it 
as an explicit equipment in its mathematical model, 
only the synthesis tool presents a commercial controller 
and includes it during the cost analysis. Therefore, 
the formal synthesis method presents more reliable results than
HOME Pro.

Case study $7$ was not solved by the synthesis tool 
within the time limit established during the experimental 
phase. Case study $3$ was not possible to simulate in HOMER Pro, 
because its restriction does not allow one to set the battery autonomy, 
thus resting both without parameters to comparative.

Summarizing, the synthesis tool is capable to present a 
solution, which is far detailed and close to the commercial 
reality than the solution presented by HOMER Pro. 
In particular, the automated synthesis method 
can provide all the details of every component of 
a PV system solution, with complete electrical details 
from data sheet of manufacturers, including 
the model of the component, nominal current and voltage. 
In this respect, even the name of the manufacturer 
can be presented (in Table~\ref{tab1} it was removed 
to avoid some advertising).
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

@@

At this Section, it was reported a favorable assessment of proposed formal synthesis method. 
Nevertheless, it was also identified three threats to the validity 
of the experimental results, which can be further assessed and 
constitute future work:

\begin{itemize}
\item ($1$) improvement of the power reliability 
analysis: to include loss of load probability or loss of power 
supply probability, which can make the analysis more accurate; 
\item ($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
however, a broad analysis from other isolated areas must be 
performed in order to make the optimization general in terms 
of applicability; 
\item ($3$) to deploy at the field some PV systems 
sized using the synthesized results in order to validate it.
\end{itemize}
